Remark on the hypothetical judgment

### 2015-08-01 paper.tex
...

\begin{quote}
$\IsTrue{\Imp{P}{Q}}$ may be asserted if and only if we
possess a construction $r$, which, joined to any demonstration of $\IsTrue{P}$,
would automatically effect a demonstration of $\IsTrue{Q}$.
\end{quote}

>>>>

\begin{quote}
$\IsTrue{\Imp{P}{Q}}$ may be asserted if and only if we
possess a construction $\mathfrak{r}$, which, joined to any demonstration of $\IsTrue{P}$,
would automatically effect a demonstration of $\IsTrue{Q}$.
\end{quote}
